\section{Context}
\begin{itemize}
    \item \textbf{The embedded vehicle system} Legacy in-vehicle networks (Classical CAN at 1 Mbit/s, LIN at 20 Kbit/s) were never designed for high-volume continuous sensor streams (video, radar point clouds). \citep{bello2019}. \textit{Questions to be answered here:} What is an (in-vehicle) embedded system? What role do in-vehicle networks play? 
    \item \textbf{Event-based logging} Event-triggered control and logging originate in embedded real-time systems. \textit{Questions to be answered here:} What is event-based loggin? Why was it invented? What limitations does it have?
    \item \textbf{The question of data} The rise of ADAS and distributed perception drives exponential sensor data growth. \textit{Questions to be answered here:} Do modern vehicles produce more data? 
    \item \textbf{The importance of down stream machine learning tasks} ML-based predictive maintenance \citep{theissler2021}, intrusion detection \citep{ozdemir2024}, and fleet analytics \citep{mdpi2024} rely on continuous, unbiased data. \textit{Questions to be answered here:} How relevant are down-stream machine learning tasks for modern vehicle systems? 
    \item \textbf{Emerging research directions:} \textit{Questions to be answered here:} What research has been done around this topic?
    \begin{itemize}
        \item \emph{Utility-aware adaptive telemetry:} Log data based on novelty or uncertainty \citep{wiessner2024}.
        \item \emph{End-to-end co-design:} Treat logging and ML inference as a coupled optimization loop \citep{task_oriented2023}.
        \item \emph{Task-aware tokenization:} Learn discrete, information-rich representations that maximize ML utility per bit \citep{tokenization2024, dataset_distillation2025}.
    \end{itemize}
\end{itemize}